Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-25 paper.tex
finished intro summary

        In sec

>>>>

        Big Data frameworks differ from those available in neuroimaging as their
        focus is mainly on workflow composition and performance. Big Data 
        frameworks such as Apache Spark and Dask both aim to be easy-to-use,
        applicable to a wide variety of analyses and improve performance in the 
        processing of Big Data. These types of systems were primarily designed 
        to be efficient on commodity infrastructure in which transferring data
        over a network would be extremely costly.

        Currently, there exists no Big Data framework which is adapted for the
        processing of neuroimaging data. However, tools such as the Thunder 
        Project \note{add citation} allow for the processing of time-series
        neuroimaging data using Spark as the backend framework. Tools such as 
        these provide built-in functions to process the data. For users to 
        extend functionality, it is necessary for them to understand the backend
        framework. Other scientific workflow engines, such as Toil and Pegasus
        \note{add citations}, have incorporated features that enable more 
        performant workflow executions for scientific Big Data. They also enable
        the integration of Big Data frameworks as subpipelines within their 
        workflows. Despite integration with Big Data frameworks, it is not
        possible to create Big Data workflows using their API exclusively.

        A big limitation to adapting Big Data frameworks for neuroimaging 
        workflows is that these frameworks are tightly-coupled with the 
        infrastructure they were designed for -- commodity clusters. While
        it is possible for some research labs to be using either a local cluster
        or the cloud for their processing, many may only have access to HPC
        clusters. As a result of this, most available scientific workflow 
        frameworks have been designed for processing on HPC clusters. The 
        set-up of an HPC cluster is quite different from that of a commodity 
        cluster, and therefore, in order to effectively use Big Data frameworks
        for scientific computing, it is necessary to adapt the infrastructure 
        for processing on HPC.

        In section \ref{datasets}, we will briefly discuss the two types of 
        datasets that are giving rise to the neuroimaging big data. Section 
        \ref{platforms} will provide a brief introduction to the data-sharing
        and processing platforms available to researchers. We will conclude our 
        introduction on the differences between commodity and HPC infrastructure
        in section \ref{infrastructure}.

        As we wish to evaluate and compare scientific workflow frameworks with
        Big Data frameworks for the processing of neuroimaging big data, we will
        break down our analyses by the four principal features necessary for
        effective neuroimaging workflow engines. The workflow engines discussed
        will include SPM, LONI, Nipype, PSOM, FastR, AA, Pydpiper 
        for neuroimaging; Taverna, Pegasus, Make, OpenMOLE, Nextflow, Galaxy, 
        Toil for other scientific workflows; and MapReduce, Spark and Dask for
        Big Data Frameworks. Chapter \ref{workcomp} will evaluate these 
        workflows on the basis of workflow composition. In other words, we will
        look at the programming languages necessary to construct these workflows
        , how easy is it to add new tools and will these workflows be understood
        by the community. In Chapter \ref{performance}, we will proceed to 
        investigate the strategies employed by these frameworks to improve the 
        performance of their workflows. Chapter \ref{portability} will discuss
        the portability of the workflows written using these frameworks. 
        Workflow reproducibility will be then discussed in Chapter 
        \ref{reproducibility}.
